---
title: "Decorate Module Output"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Decorate Module Output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(teal.goshawk)
```

## Introduction

The outputs produced by `teal` modules, like graphs or tables, are created by the module developer and look a certain way.
It is hard to design an output that will satisfy every possible user, so the form of the output should be considered a default value that can be customized.
Here we describe the concept of _decoration_, enabling the app developer to tailor outputs to their specific requirements without rewriting the original module code.

The decoration process is build upon transformation procedures, introduced in `teal`.
While `transformators` are meant to edit module's input, decorators are meant to adjust the module's output.
To distinguish the difference, modules in  `teal.goshawk` have 2 separate parameters:
`transformators` and `decorators`.

To get a complete understanding refer the following vignettes:

- Transforming the input data in
[this vignette](https://insightsengineering.github.io/teal/latest-tag/articles/transform-input-data.html).
- Transforming module output in [this vignette](https://insightsengineering.github.io/teal/latest-tag/articles/transform-module-output.html).

## Outputs that can be decorated

It is important to note which output objects from a given module can be decorated.
The module function documentation's _Decorating Module_ section has this information.

You can also refer the table shown below to know which module outputs can be decorated.


| Module                           | Output (Class) |
|----------------------------------|----------------|
| `tm_g_gh_boxplot`                | plot (`ggplot`)  |
| `tm_g_gh_correlationplot`        | plot (`ggplot`)  |
| `tm_g_gh_density_distribution_plot` | plot (`ggplot`)  |
| `tm_g_gh_lineplot`               | plot (`ggplot`)  |
| `tm_g_gh_spaghettiplot`          | plot (`ggplot`)  |

## Decorating `ggplot`

Here's an example to showcase how you can edit an output of class `ggplot`.
You can extend them using `ggplot2` functions.

```{r decorate_ggplot, message=FALSE, eval = FALSE}
data <- within(teal_data(), {
  library(dplyr)
  library(nestcolor)
  library(stringr)
  # use non-exported function from goshawk
  .h_identify_loq_values <- getFromNamespace("h_identify_loq_values", "goshawk")
  # original ARM value = dose value
  .arm_mapping <- list(
    "A: Drug X" = "150mg QD",
    "B: Placebo" = "Placebo",
    "C: Combination" = "Combination"
  )
  ADSL <- teal.data::rADSL
  ADLB <- teal.data::rADLB
  .var_labels <- lapply(ADLB, function(x) attributes(x)$label)
  ADLB <- ADLB %>%
    mutate(
      AVISITCD = case_when(
        AVISIT == "SCREENING" ~ "SCR",
        AVISIT == "BASELINE" ~ "BL",
        grepl("WEEK", AVISIT) ~ paste("W", str_extract(AVISIT, "(?<=(WEEK ))[0-9]+")),
        TRUE ~ as.character(NA)
      ),
      AVISITCDN = case_when(
        AVISITCD == "SCR" ~ -2,
        AVISITCD == "BL" ~ 0,
        grepl("W", AVISITCD) ~ as.numeric(gsub("[^0-9]*", "", AVISITCD)),
        TRUE ~ as.numeric(NA)
      ),
      AVISITCD = factor(AVISITCD) %>% reorder(AVISITCDN),
      TRTORD = case_when(
        ARMCD == "ARM C" ~ 1,
        ARMCD == "ARM B" ~ 2,
        ARMCD == "ARM A" ~ 3
      ),
      ARM = as.character(.arm_mapping[match(ARM, names(.arm_mapping))]),
      ARM = factor(ARM) %>% reorder(TRTORD),
      ACTARM = as.character(.arm_mapping[match(ACTARM, names(.arm_mapping))]),
      ACTARM = factor(ACTARM) %>% reorder(TRTORD),
      ANRLO = 50,
      ANRHI = 75
    ) %>%
    rowwise() %>%
    group_by(PARAMCD) %>%
    mutate(LBSTRESC = ifelse(
      USUBJID %in% sample(USUBJID, 1, replace = TRUE),
      paste("<", round(runif(1, min = 25, max = 30))), LBSTRESC
    )) %>%
    mutate(LBSTRESC = ifelse(
      USUBJID %in% sample(USUBJID, 1, replace = TRUE),
      paste(">", round(runif(1, min = 70, max = 75))), LBSTRESC
    )) %>%
    ungroup()
  # add LLOQ and ULOQ variables
  ALB_LOQS <- .h_identify_loq_values(ADLB, "LOQFL")
  ADLB <- left_join(ADLB, ALB_LOQS, by = "PARAM")
})

join_keys(data) <- default_cdisc_join_keys[names(data)]

app <- init(
  data = data,
  modules = modules(
    tm_g_gh_boxplot(
      label = "Box Plot",
      dataname = "ADLB",
      param = picks(
        variables("PARAMCD", "PARAMCD"),
        values(selected = "ALT", multiple = FALSE),
        check_dataset = FALSE
      ),
      yaxis_var = variables(c("AVAL", "BASE", "CHG"), "AVAL"),
      xaxis_var = variables(c("ACTARM", "ARM", "AVISITCD", "STUDYID"), "ARM"),
      facet_var = variables(c("ACTARM", "ARM", "AVISITCD", "SEX"), "AVISITCD"),
      trt_group = variables(c("ARM", "ACTARM"), "ARM"),
      loq_legend = TRUE,
      rotate_xlab = FALSE,
      hline_arb = c(60, 55),
      hline_arb_color = c("grey", "red"),
      hline_arb_label = c("default_hori_A", "default_hori_B"),
      hline_vars = c("ANRHI", "ANRLO", "ULOQN", "LLOQN"),
      hline_vars_colors = c("pink", "brown", "purple", "black"),
      decorators = list(plot = ggplot_caption_decorator("I am a ggplot"))
    )
  )
)
if (interactive()) {
  shinyApp(app$ui, app$server)
}
```
